---
title: "Journal (reproducible report)"
author: "Alexander Sowarka"
date: "2020-11-30"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Intro to tidyverse Challenge

Last compiled: `r Sys.Date()`

## Given Code
Following given code chunks from the exercise are used:
```{r}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)
library(lubridate)

# 2.0 Importing Files ----
# A good convention is to use the file name and suffix it with tbl for the data structure tibble
bikes_tbl      <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")

# Not necessary for this analysis, but for the sake of completeness
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

# 3.0 Examining Data ----


# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

# Examine the results with glimpse()
bike_orderlines_joined_tbl %>% glimpse()

# 5.0 Wrangling Data ----
# All actions are chained with the pipe already. You can perform each step separately and use glimpse() or View() to validate your code. Store the result in a variable at the end of the steps.
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 5.1 Separate category name
separate(col    = category,
         into   = c("category.1", "category.2", "category.3"),
         sep    = " - ") %>%

# 5.2 Add the total price (price * quantity) 
# Add a column to a tibble that uses a formula-style calculation of other columns
mutate(total.price = price * quantity) %>%

# 5.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
# 5.3.1 by exact column name
select(-...1, -gender) %>%

# 5.3.2 by a pattern
# You can use the select_helpers to define patterns. 
# Type ?ends_with and click on Select helpers in the documentation
select(-ends_with(".id")) %>%

# 5.3.3 Actually we need the column "order.id". Let's bind it back to the data
bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 

# 5.3.4 You can reorder the data by selecting the columns in your desired order.
# You can use select_helpers like contains() or everything()
select(order.id, contains("order"), contains("model"), contains("category"),
       price, quantity, total.price,
       everything()) %>%

# 5.4 Rename columns because we actually wanted underscores instead of the dots
# (one at the time vs. multiple at once)
rename(bikeshop = name) %>%
set_names(names(.) %>% str_replace_all("\\.", "_"))
```

## Data Wrangling

For the challenge first the data wrangling needs to be adapted to separate the location attribute into city and state:

```{r}
bike_orderlines_wrangled_tbl <- bike_orderlines_wrangled_tbl %>%
# 5.5 Separate Location into State and City
separate(col    = location,
         into   = c("city", "state"),
         sep    = ", " )
bike_orderlines_wrangled_tbl
```

## Buiseness Insights - Sales by State
### Data Manipulation
The data must be grouped by the new created state column and then the sales must be summarised. This results in the sales per state.
```{r}
sales_by_loc_tbl <- bike_orderlines_wrangled_tbl %>%
  
# Select state and price
select(state, total_price) %>%

# Group by State
group_by(state) %>%
summarise(sales = sum(total_price)) %>%
ungroup() %>%

# Format $ Text
mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                   decimal.mark = ",", 
                                   prefix = "", 
                                   suffix = " €"))

sales_by_loc_tbl
```

### Data Visualization
For plotting the following code can be used:
```{r, fig.width=10, fig.height=7}
sales_by_loc_tbl %>%
  
# Setup canvas with the columns year (x-axis) and sales (y-axis)
ggplot(aes(x = state, y = sales)) +

# Geometries
geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot

  # Theme
theme(axis.text.x = element_text(angle = 45, hjust = 1)) +

# Formatting
scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                  decimal.mark = ",", 
                                                  prefix = "", 
                                                  suffix = " €")) +
labs(
  title = "Revenue by State",
  x = "State", # Override defaults for x and y
  y = "Revenue"
)
```

## Buiseness Insights - Sales by State and Year
### Data Manipulation
The data must be grouped by the new created state column and newly created year column and then the sales must be summarised. This results in the sales per state and year.
```{r}
sales_by_loc_year_tbl <- bike_orderlines_wrangled_tbl %>%
  
# Select state and price and add a year
select(order_date, state, total_price) %>%
mutate(year = year(order_date)) %>%

# Group by State
group_by(year, state) %>%
summarise(sales = sum(total_price)) %>%
ungroup() %>%

# Format $ Text
mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                   decimal.mark = ",", 
                                   prefix = "", 
                                   suffix = " €"))

sales_by_loc_year_tbl  
```

### Data Visualization
For plotting the following code can be used:
```{r, fig.width=10, fig.height=7}
sales_by_loc_year_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Use geom_col for a bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  # Theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by State",
    x = "", # Override defaults for x and y
    y = "Revenue",
    fill = "State"
  )
```
